Greenhouse gas emissions model - making scenarios

### 2021-11-01 GHG_model_report.Rmd
Rename and shft files for clarity, update readme with indications about files

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(plyr)
library(rmarkdown)
#devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data}
library(DiagrammeR)
library(decisionSupport)
library(plyr)
library(magrittr)
library(kableExtra)
### # This project will be stored in relative file paths (i.e. same or lower folders)

@@

```{r graph-mermaid-manure, echo=FALSE, fig.width=10, fig.height=1, include = F}
mermaid("
        graph LR
        C(Central collection)-->B(Burned); linkStyle 0 stroke: red, stroke-width:1px
                                B-->P(Pasture); linkStyle 1 stroke: red, stroke-width:1px
        C-->D(Daily spread); linkStyle 2 stroke: green, stroke-width:1px
            D-->S(Sold); linkStyle 3 stroke: red, stroke-width:1px
                S-->L(Liquid storage); linkStyle 4 stroke: red, stroke-width:1px
                    L-->Co(Composted); linkStyle 5 stroke: red, stroke-width:1px
                        Co-->Dl(Dry lot); linkStyle 6 stroke: red, stroke-width:1px
                             Dl-->St(Solid storage); linkStyle 7 stroke: red, stroke-width:1px
                    L-->Bi(Biogas); linkStyle 8 stroke: green, stroke-width:1px
                        Bi-->Ls(Liquid slurry); linkStyle 9 stroke: red, stroke-width:1px
        ")
```

>>>>

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
#devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data}
### # This project will be stored in relative file paths (i.e. same or lower folders)

@@

```{r graph-mermaid-manure, echo=FALSE, fig.width=10, fig.height=1}
mermaid("
        graph LR
        C(Central collection)-->B(Burned); linkStyle 0 stroke: red, stroke-width:1px
                                B-->P(Pasture); linkStyle 1 stroke: red, stroke-width:1px
        C-->D(Daily spread); linkStyle 2 stroke: green, stroke-width:1px
            D-->S(Sold); linkStyle 3 stroke: red, stroke-width:1px
                S-->L(Liquid storage); linkStyle 4 stroke: red, stroke-width:1px
                    L-->Co(Composted); linkStyle 5 stroke: red, stroke-width:1px
                        Co-->Dl(Dry lot); linkStyle 6 stroke: red, stroke-width:1px
                             Dl-->St(Solid storage); linkStyle 7 stroke: red, stroke-width:1px
                    L-->Bi(Biogas); linkStyle 8 stroke: green, stroke-width:1px
                        Bi-->Ls(Liquid slurry); linkStyle 9 stroke: red, stroke-width:1px
        ")
```

### 2021-11-01 Scenarios_report.Rmd
Rename and shft files for clarity, update readme with indications about files

We're defining the function as in the 'Greenhouse gas emissions model' document. Please look there for more inforamtion about the original model design.

@@

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data, include=FALSE}
library(DiagrammeR)
library(decisionSupport)
library(plyr)
library(magrittr)
library(kableExtra)
### # This project will be stored in relative file paths (i.e. same or lower folders)

>>>>

We're defining the function as in the ['Greenhouse gas emissions model']() document. Please look there for more information about the original model design.

@@

```{r, warning=FALSE, include=FALSE}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data, include=FALSE}

### # This project will be stored in relative file paths (i.e. same or lower folders)
